---
title: "Homework6"
author: "Yuxin"
date: "2018.11.24"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(purrr)
```

# Problem 1

## Part1: Read and clean data
```{r}
homicide_url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicide_data = read.csv(url(homicide_url)) %>%
  janitor::clean_names() %>%
  as_tibble()

### Create a new variable containes city and state
homicide_data = homicide_data %>%
  mutate(city_state = str_c(city, state, sep = ", " )) %>%
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))


### Modifiy variable race and age
homicide_data = homicide_data %>%
  mutate(solved = as.numeric(disposition == "Closed by arrest"),
         victim_race = ifelse(victim_race == "White", "white", "non-white"),
         victim_race = fct_relevel(victim_race, ref = "white"),
         victim_age = as.numeric(victim_age))
```

## Part2: Fit a model for Baltimore
```{r}
homicide_baltimore = homicide_data %>%
  filter(city_state == "Baltimore, MD")
fit_logistic = homicide_baltimore %>%
  glm(solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())


fit_logistic %>% 
  broom::tidy() %>% 
  select(term, estimate, std.error) %>%
  mutate(Term = recode(term, "victim_racenon-white" = "victim_race: non-white", "victim_sexMale" = "victim_sex: male"), 
         "Odds Ratio" = exp(estimate), 
         "Lower bound" = exp(estimate -1.96*std.error), 
         "Upper bound" = exp(estimate +1.96*std.error)) %>%
  select(Term, "Odds Ratio", "Lower bound", "Upper bound") %>%
  knitr::kable(digits = 3)
```

## Part3: Fit the model for all cities
```{r}

### Write a function to fit the model 
logistic_fit = function(df){
 glm(solved ~victim_age + victim_race + victim_sex, data =df, family = binomial()) %>%
 broom::tidy() %>%
 mutate(ors = exp(estimate),
        conf_low = exp(estimate -1.96*std.error),
        conf_high = exp(estimate +1.96*std.error)) %>%
    select(term, ors, conf_low, conf_high) %>%
    filter(term == "victim_racenon-white")
}
  
## Fit the model
homicide_city = homicide_data %>%
  select(city_state, solved, victim_sex, victim_race, victim_age) %>%
  group_by(city_state) %>%
  filter(victim_sex %in% c("Female", "Male", "Unknown")) %>% 
  nest() %>%
  mutate(log_models = map(data, logistic_fit)) %>%
  select(-data) %>%
  unnest()
```

## Part4: Create a plot for each city
```{r}
homicide_city %>%
  ggplot(aes(x = fct_reorder(city_state, ors), y = ors, color = city_state))+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high, width = 0.2))+
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        legend.position = "none")+
  labs(title = "Estimated odds ratio of Non-white to White victims for solving homicidies among 50 large cities",
       x = "City, State",
       y = "Adjusted odds ratio")
  
```

This the plot that shows the odds ratio and 95% confidence interval of non-white to white victims for solving homicides in 50 large U.S. cities. We can observe that Tampa have the highest odds ratios and Durham has the highest confidence bands. Futhermore, we can observe that there exist some 95 confidence interval such that upper bound is less than 1. We can conclude that for those cities, we are 95% confident that nonwhites have a lower proportion of unsolved homicides than whites. Also, there does not exist 95 confidence interval such that lower bound is biger than 1. We cannot conclude that nonwhites have a higher proortion of unsolved homicides than whites of all cities.

# Problem 2

## Part1 Read and clean data
```{r}
birthweight_data = read_csv(file = "./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))
### Check for missing values
colSums(is.na(birthweight_data))
```
We can see that there is no missing data.

## Part2 Propose a regression model for birthweight
```{r}
fit_null = lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + wtgain, data = birthweight_data)
birthweight_data %>%
  add_predictions(fit_null) %>%
  add_residuals (fit_null) %>%
  ggplot(aes(x = pred, y = resid))+
  geom_point(alpha = 0.2) +
  labs( title = " Residuals vs. Predicted Values",
          x = "Predicted Values",
          y = "Residauls"
    
  )
```

For the question, I choose a regression model based on a hypothesized structure for the factor. I choose six variables which may have direct relationship with the infant's birthweight. They are babysex, babyhead, baby's length, mother's weight at delivery, gestational age in weeks and mother's weight gain during pregnancy. From the residual vs prediction plots, we can observed that most obsrevation are located in the lower right. The residuals are roughly symmetrically distributed around zero. We may compare with other models to do further inference. 

## Part3 Compare with other models
```{r}
## Two extrea models
fit_main = lm(bwt ~ blength + gaweeks, data = birthweight_data)
fit_int = lm(bwt ~ bhead + blength + babysex + (bhead * blength) + (bhead * babysex) + (blength * babysex) +(bhead * babysex * blength), data = birthweight_data)

## Compare two models
cv_birthweight = crossv_mc(birthweight_data, 100)

cv_birthweight = cv_birthweight %>%
  mutate(fit_null = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + wtgain, data = birthweight_data)),
         fit_main = map(train, ~lm(bwt ~ blength + gaweeks, data = birthweight_data)),
         fit_int = map(train, ~lm(bwt ~ bhead + blength + babysex + (bhead * blength) + (bhead * babysex) + (blength * babysex) +(bhead * babysex * blength), data = birthweight_data))) %>%
  mutate(rmse_null = map2_dbl(fit_null, test, ~rmse(model = .x, data = .y)),
         rmse_main = map2_dbl(fit_main, test, ~rmse(model = .x, data = .y)),
         rmse_int = map2_dbl(fit_int, test, ~rmse(model = .x, data = .y)))

```
